Dynamical Properties of Molecular-forming Gas Clumps in Galaxies at the Epoch of Reionization

### 2020-04-20 WRITEUP/ms_referee2.tex
w/ MMM edits

% ------------------
\section{Numerical Simulations}\label{sec:sim}
The simulations used in this work are described by \citet{Pallottini17a, Pallottini17b} and are briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian.} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$
at {\bf $z$\eq6}. The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$. This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryonic) mass exceeds the mass resolution by a factor of eight. The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e., sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},

@@

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun 
(see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a})\footnote{{\bf The stellar mass-to-halo mass ratio for Althaea at $z$\eq6 is about 0.07. 
This is a factor of about 3 higher than the typical value inferred by abundance matching models, that typically gives $\sim0.02$. 
Note however that the ratio from abundance matching can vary; for instance, \citet{Behroozi13b} (main method) finds a ratio of 0.015\,--\,0.025 
is for a halo mass between $M_{\rm halo}$\ssim10$^{10.5}$--$10^{12}$\,\Msun, whereas in the same paper the authors find 
0.01--0.05 in the same mass range from direct abundance matching 
(see the Appendix therein). 
Additionally, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, i.e., within a factor 3 from \citet{Behroozi13b}.}.} 
The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.

@@

{\bf As seen in \Sec{dist}, the cuts used to identify the molecular structures are based on the H$_2$ number density, which ranges from 
n$_{\rm H2}$\ssim0.1\,--\,30\,\cc. We do not explicitly use a minimum H$_2$ fraction to select the structures. 
Among the various cuts, two physical regimes are identified, corresponding to materials in the disk/interarm material and MGCs (see Fig. 5). 
The former with n$_{\rm gas}<100$\,\cc and n$_{\rm H2} < 5$\,\cc, whereas the latter with 
n$_{\rm gas}$\ssim$100$\,\cc and n$_{\rm H2} \gtrsim10$\,\cc (see also Fig. 5 of \citet{Pallottini17b} 
for details\footnote{In particular, with their analysis of the Minkowski function of the molecular density field (see Fig. 6 therein)}). 
Considering that $f_{\rm H2}$\eq$\rho_{\rm H2} / \rho_{\rm H,total}$\eq$\rho_{\rm H2}/(\mu \rho_{\rm gas})$\eq
$m_{\rm H2} n_{\rm H2} / m_p~\mu~n_{\rm gas}$\ssim2 $n_{\rm H2}/(0.7~n_{\rm gas})$, 
for the disk/interarm, $f_{\rm H2}$\ssim14\% and for the MCCs, $f_{\rm H2}$\ssim28\%. 
Note that for the lowest value of the H2 cuts, this fraction might be lower; however, 
removing regions selected with such cuts yields no qualitative change to the physical interpretation resulting from the analysis.}

@@

\section*{Acknowledgements}
We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Caitlin Casey for useful discussions.
%
TKDL gratefully acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
% mm
M-MML acknowledges partial support by the NSF through award
AST18-15461, and hospitality from the Insitute for Theoretical
Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
The Flatiron Institute is funded by the Simons Foundation.
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
\software{Python \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{PyMSES} \citep{Labadens2012}, SciPy \citep{scipyref}, and yt \citep{Smith09a,Turk11a}}

>>>>

% ------------------
\section{Numerical Simulations}\label{sec:sim}
The simulations used in this work are described by \citet{Pallottini17a, Pallottini17b} and are briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in Italian.} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) techniques to achieve high spatial resolution in regions of interest (e.g., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size. The simulation zooms in on a target halo of mass $M_{\rm DM}\simeq10^{11} \Msun$
at $z$\eq6. The Lagrangian region of the halo (2.1\,Mpc $h$\pmOne) has a dark matter mass resolution of $\simeq 6\times 10^4 \Msun$, equivalent at initial density to a baryonic mass resolution of $1.2 \times 10^4 \Msun$. This region is spatially refined with a quasi-Lagrangian criterion based on a mass threshold, so that a cell is refined if its total (dark+baryonic) mass exceeds the mass resolution by a factor of eight. The finest refined cell allowed in the zoom in region has size $l_{\rm cell}\simeq$\,30\,pc (at $z = 6$), i.e., sizes are comparable to the sizes of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a},

@@

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass
$M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of $M_\star\simeq$\,2.6\E{10}\,\Msun, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
Abundance matching of halos shows that this ratio varies as the halo mass becomes much larger or smaller than from $M_h$\ssim10$^{12}$\,\Msun
(see \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a})\footnote{{\bf The stellar mass-to-halo mass ratio for Althaea at $z$\eq6 is about 0.07.
This is a factor of about three higher than the typical value inferred by abundance matching models, which typically give values of $\sim0.02$.
Note however that the ratio from abundance matching can vary; for instance, \citet{Behroozi13b} (main method) finds a ratio of 0.015\,--\,0.025
for a halo mass between $M_{\rm halo}$\ssim10$^{10.5}$--$10^{12}$\,\Msun, whereas in the same paper the authors find
0.01--0.05 in the same mass range from direct abundance matching
(see the Appendix therein).
As another example, from an earlier abundance matching study, \citet{Moster13a} find a ratio 0.005, also differing by a factor three from \citet{Behroozi13b}, though in opposite direction}.}
The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.

@@

{\bf As seen in \Sec{dist}, the cuts used to identify the molecular structures are based on the H$_2$ number density, which ranges from
n$_{\rm H2}$\ssim0.1\,--\,30\,\cc. We do not explicitly use a minimum H$_2$ fraction to select the structures.
Among the various cuts, two physical regimes are identified, corresponding to materials in the disk/interarm material and MGCs (see Fig. 5).
The former have n$_{\rm gas}<100$\,\cc and n$_{\rm H2} < 5$\,\cc, whereas the latter have
n$_{\rm gas}$\ssim$100$\,\cc and n$_{\rm H2} \gtrsim10$\,\cc (see also Figs. 5 and 6 of \citet{Pallottini17b}
for details\footnote{In particular, their analysis of the Minkowski function of the molecular density field (see Fig. 6 therein)}).
Considering that $f_{\rm H2}$\eq$\rho_{\rm H2} / \rho_{\rm H,total}$\eq$\rho_{\rm H2}/(\mu \rho_{\rm gas})$\eq
$m_{\rm H2} n_{\rm H2} / (m_p\,\mu\,n_{\rm gas})$\ssim2 $n_{\rm H2}/(0.7~n_{\rm gas})$,
for the disk/interarm region $f_{\rm H2}$\ssim14\%, while for the MGCs $f_{\rm H2}$\ssim28\%.
Note that for the lowest value of the H$_2$ cuts, these fractions might be lower; however,
removing regions selected with such cuts yields no qualitative change to the physical interpretation resulting from the analysis.}

@@

\section*{Acknowledgements}
We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, Caitlin Casey for useful discussions, and the referee for providing constructive
comments on the manuscript.
%
TKDL gratefully acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
% mm
M-MML acknowledges partial support by the NSF through award
AST18-15461, and hospitality from the Insitute for Theoretical
Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
The Flatiron Institute is funded by the Simons Foundation.
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
\software{Python \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{PyMSES} \citep{Labadens2012}, SciPy \citep{scipyref}, and yt \citep{Smith09a,Turk11a}}
